---
title: "Weight of Fish"
author: "Marcia Alarcon"
date: "Fall 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```


```{r}
Fish=read.csv("Fish.csv")
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Subset of fish that contains the species I want to analyze. Then I will look at how well each combination of the predictor variables can predict the weight of the fish. We are using the perch subset in my analysis.

```{r}
perch=filter(Fish,Species=="Perch")
```


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
basicNN <- ggplot(perch,aes(y=Weight,x=Length1))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```   


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = select (perch,-Species),
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The graph shows that the Y-axis is the adjusted R squared, and the X-axis is the number of variables used in a linear fit. The best fit comes from using two variables height and width.
  
  
```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```

The summary shows which two variables are best. Which is height and width.


```{r}
best.model <- lm(Weight~Height+Width,data=perch)
summary(best.model)
fullup=lm(Weight~.,data= select (perch, -Species))
```

We made a linear model based on the best variables height and width. The best prediction for weight=-536 + 74.77 * Height + 69.62 * width. This equation is the best fit for predicting the weight of the perch using the two variables width and Height.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

$H_0$: There is no difference between models 1 and 2 when predicting the Weight of the fish (perch).

$H_A$: There is a difference between models 1 and 2 when predicting the Weight of the fish (perch).

```{r}
anova(fullup,best.model)
```

This Analysis of Variance Table shows  that model 1 is slightly better because it has a smaller Residual sum of squares.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We fail to reject the Null Hypothesis because the P value is relativity high at 0.879. We conclude that Height and width are the two best variables when predicting weight.

# Second Fish

## Build the best regression model you can that predicts the weight of bream
## Using only two predictor variables  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Subset of fish that contains the species I want to analyze. Then I will look at how well each combination of the predictor variables can predict the weight of the fish. We are using the pike subset in my analysis.

```{r}
bream=filter(Fish,Species=="Bream")
```

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

```{r}
basicNN <- ggplot(bream,aes(y=Weight,x=Length1))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```   

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = select (bream,-Species),
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The graph shows that the Y-axis is the adjusted R squared, and the X-axis is the number of variables used in a linear fit. The best fit comes from using two variables height and width.

```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[2,]
```

The summary shows which two variables are best. Which is height and width.


```{r}
best.model <- lm(Weight~Height+Width,data=perch)
summary(best.model)
fullup=lm(Weight~.,data= select (bream, -Species))
```


We made a linear model based on the best variables height and width. The best prediction for weight=-536 + 74.77 * Height + 69.62 * width. This equation is the best fit for predicting the weight of the perch using the two variables width and Height.
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->



## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


$H_0$: There is no difference between models 1 and 2 when predicting the Weight of the fish (bream).

$H_A$: There is a difference between models 1 and 2 when predicting the Weight of the fish (bream).



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


# Third Fish
## Build the best regression model you can that predicts the weight of roach
## Using only two predictor variables  


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Subset of fish that contains the species I want to analyze. Then I will look at how well each combination of the predictor variables can predict the weight of the fish. We are using the Roach subset in my analysis.


```{r}
roach=filter(Fish,Species=="Roach")
```


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
basicNN <- ggplot(roach,aes(y=Weight,x=Length1))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```   



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = select (roach,-Species),
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The graph shows that the Y-axis is the adjusted R squared, and the X-axis is the number of variables used in a linear fit. The best fit comes from using two variables height and width.


```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```

The summary shows which two variables are best. Which is height and width.

```{r}
best.model <- lm(Weight~Height+Width,data=roach)
summary(best.model)
fullup=lm(Weight~.,data= select (roach, -Species))
```

We made a linear model based on the best variables height and width. The best prediction for weight=-286 + 9.47 * Height + 102.473 * width. This equation is the best fit for predicting the weight of the perch using the two variables width and Height.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

$H_0$: There is no difference between models 1 and 2 when predicting the Weight of the fish (roach).

$H_A$: There is a difference between models 1 and 2 when predicting the Weight of the fish (roach).



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
